---
title: "Assignment1-R Programming_Group10"
output: pdf_document
author: Group 10 - Anumol, Bruno, Clifford, Rushia, Skanda
date: "2023-02-12"
header-includes: 
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyfoot[CO,CE]{Github Repository - https://github.com/Clifford1811/BUS4066-TM10.git}
- \fancyfoot[RE,RO]{\thepage}
- \fancypagestyle{plain}{\pagestyle{fancy}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Install Packages install.packages('tidyverse') install.packages('dplyr') install.packages('magrittr') install.packages('ggplot') install.packages('xycorr')

### Import Data Set Fuel_Consumption_2000.2022.csv

```{r - import csv file or run this code to read csv file}
Fuel_Consumption_2000.2022 <- read.csv(
"C:/Users/Rushia/Downloads/Fuel_Consumption_2000-2022.csv/Fuel_Consumption_2000-2022.csv")

fuel=Fuel_Consumption_2000.2022
```

### Print the structure of dataset

```{r - print the structure of Fuel_Consumption_2000_2022}
str(fuel)
```

### List the variables in your dataset

```{r - list the variable in Fuel_Consumption_2000_2022}
names(fuel)
```

### Print the top 15 rows of your dataset

```{r - print the top 15 rows of Fuel_Consumption_2000_2022}
head(fuel, n=5)
```

### Write a user defined function using any of the variables from the data set

```{r - create function to find fuel consumption in year 2021}
FuelConsumption_Year <- function(FUEL.CONSUMPTION) {
  2021 - FUEL.CONSUMPTION
}
print(head(FuelConsumption_Year(fuel$FUEL.CONSUMPTION), N=10))
```

### Use data manipulation techniques and filter rows based on any logical criteria that exist in dataset

```{r - filter through make of vehicle for BMW cars only}
# Attach tidyverse packages to use data manipulation, reading, transforming and visualizing dataset
library("tidyverse")

filterfuel= as.data.frame(filter(fuel,fuel$MAKE=="BMW"))
fuel %>% filter(MAKE=="BMW") %>% slice_head(n = 10)
```

### Identify the dependent & independent variables and use reshaping techniques and create a new data frame by joining those variables from dataset

```{r - use reshaping techniques and create a new data frame by joining variables}
# Create a new data frame with MAKE and MODEL column
Col_Make_Model <- cbind(fuel$MAKE, fuel$MODEL)
print(head(Col_Make_Model, n = 4))

# Find vehicles whose make is AUDI
df_make_is_Audi <- fuel %>%
                filter(MAKE=="Audi")

# Find vehicles whose model is A4
df_model_is_A4 <- fuel %>%
                filter(MAKE=="A4")

# Create a new data frame with patients whose age under 30 by merging 2 prepared data frame
df_make_Audi_model_A4 <- rbind(df_make_is_Audi, df_model_is_A4)
print(head(df_make_Audi_model_A4, n = 2))
```

### Remove missing values in your dataset

```{r - Remove missing values in Fuel_Consumption_2000.@022}
newfuel=fuel
newfuel%>%filter(!is.na(MAKE)) %>% slice_head(n = 5)
```

### Identify and remove duplicated data in dataset

```{r - identify and remove duplicated in Fuel_Consumption_2000.2022}
fuel%>%distinct(YEAR, MAKE, MODEL, ENGINE.SIZE,TRANSMISSION,FUEL, keep_all=TRUE) %>% slice_head(n = 10)
```

### Reorder multiple rows in descending order

```{r - arrange emissions in descending order}
fuel%>%arrange(desc(EMISSIONS)) %>% slice_head(n = 6)
```

### Rename some of the column names in dataset

```{r - rename column YEAR}
names(fuel)[names(fuel) == "YEAR"] <- "Year"  
```

### Add new variables in data frame by using a mathematical function

```{r - create a new variable that preserves existing ones to calculates Emission By Year}
fuel %>% filter(!is.na(EMISSIONS)) %>% mutate(mathf= 2000 - EMISSIONS) %>% slice_head(n=10) 
```

### Create a training set using random number generator engine

```{r - training set using random number generator engine}
#Extract 3 random rows without replacement
fuel %>% sample_n(8, replace=FALSE)

#Select top 2 rows ordered by a variable
fuel %>% top_n(2, FUEL.CONSUMPTION)
```

### Print the summary statistics of dataset

```{r - find mean fuel consumption of each make}
fuel %>% group_by(MAKE) %>% summarise(mean(FUEL.CONSUMPTION)) %>% slice_head(n=6)
```

### Use any of the numerical variables from the dataset and perform the following statistical functions: Mean, Median, Mode, Range

```{r - perform statistical functions}
# Find mean of emissions
mean(fuel[["EMISSIONS"]])

# Find median of emissions
median(fuel[["EMISSIONS"]])

# Find mode of emissions
cal_mode <- function(v) {
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}
mode(fuel[["Emissions"]])

# Find range of claim
print(range(fuel[["EMISSIONS"]]))
```

### Plot a scatter plot for any 2 variables in dataset

```{r - plot a scatter plot for fuel consumption and cylinder}
ggplot(data = fuel,aes(x = FUEL.CONSUMPTION,y = CYLINDERS ,col = factor(Year)))+geom_point()
```

### Plot a bar plot for any 2 variables in dataset

```{r - plot a bar plot for year and make}
ggplot(data = fuel,aes(x = Year,fill = factor(MAKE)))+geom_bar()
```

### Find the correlation between any 2 variables by applying least square linear regression model

```{r - find the correlation between model and year}
xycorr = cor(fuel$Year, fuel$EMISSIONS, method="pearson")
print(xycorr)
```
